---
title: "Miscellaneous R script chunks"
author: "Dr Irina Chis Ster"
date: "21/01/2021"
output:
  html_notebook:
    df_print: paged
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 72
---



### Knitting package   
 
This is needed for filles knitting and producing html notebook style file.
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

### Check the R version   

This part checks the version of R needed for the packages installation.
```{r Check R version}
if (grepl("Linux stats3", system("uname -a", intern=T))) {
  if (R.version$version.string != "R version 3.5.3 (2019-03-11)"){
    stop("Please choose R version 3.5.3 using the dropdown menu in the top right corner of RStudio Server.")
  } else {
    cat("R version correct!")
  }
}
```

### Packages

When working on RStudio Server, packages will be loaded from a
shared server drive.\
Otherwise, packages will be installed/loaded  on your local computer.

```{r}
if (grepl("Linux stats3", system("uname -a", intern=T))) {
  lib_loc <- "/homes/homedirs18/sghms/bms/shares/bdib/BDiB_2020-21/R/packages_R_3.5.3"
  stopifnot(file.exists(lib_loc))
  library(paran, lib.loc = lib_loc)
  
  library(ggplot2, lib.loc = lib_loc)
  library(emmeans, lib.loc = lib_loc)
  library(exact2x2, lib.loc = lib_loc)
  library(plyr, lib.loc = lib_loc)
  library(rstudioapi, lib.loc = lib_loc)
  library(magrittr, lib.loc = lib_loc)
  library(car, lib.loc = lib_loc)
  ##library(ggpubr, lib.loc = lib_loc)
  ##library(rstatix, lib.loc = lib_loc)
  ##library(DescTools, lib.loc = lib_loc)
  rm(lib_loc)
} else {
  
  if (!require(paran)) install.packages("paran")
  
  if (!require(emmeans)) install.packages("emmeans")
  if (!require(car)) install.packages("car")
  if (!require(exact2x2)) install.packages("exact2x2")
  if (!require(ggplot2)) install.packages("ggplot2")
  if (!require(plyr)) install.packages("plyr")
  if (!require(rstudioapi)) install.packages("rstudioapi")
  if (!require(magrittr)) install.packages("magrittr")
  ##if (!require(DescTools)) install.packages("DescTools")
  ##if (!require(rstatix)) install.packages("rstatix")
  ##if (!require(ggpubr)) install.packages("ggpubr")

}
```

### Current script file

```{r}
this.script <- basename(rstudioapi::getActiveDocumentContext()$path)
cat("Current script:", this.script)

```
